\chapter{Challenges}
\label{ch:challenges}


\section{Common Image Defects}
\label{sec:common-image-defects}

\subsection{Blurriness}
\label{subsec:blurriness}

\subsection{Noise}
\label{subsec:noise}

\subsection{Occlusion}
\label{subsec:occlusion}

\subsection{Distortion}
\label{subsec:distortion}

\subsection{Low Resolution}
\label{subsec:low-resolution}


\section{Composition of distortion effects}
\label{sec:composition-of-distortion-effects}


\section{Solving for low-level Devices}
\label{sec:solving-for-low-level-devices}

\subsection{Understanding Resource Constraints on Raspberry Pi and Similar Devices}
\label{subsec:understanding-resource-constraints-on-raspberry-pi-and-similar-devices}


Detail the hardware limitations of Raspberry Pi, such as CPU/GPU performance, memory capacity, and power consumption.

\subsection{Model Optimization}
\label{subsec:model-optimization}


\item Quantization: Reducing the precision of model weights (e.g., from 32-bit to 8-bit) to decrease memory usage
and speed up inference.
\item Pruning: Removing redundant or less significant weights from the model to streamline its structure.
\item Knowledge Distillation: Training a smaller model to replicate the performance of a larger mode,
maintaining accuracy while reducing complexity.

\subsection{Efficient Image Processing Algorithms}
\label{subsec:efficient-image-processing-algorithms}

\subsubsection{Lightweight Super-Resolution}

\item Algorithms like SRCNN or ESPCN that offer super-resolution capabilities with lower computational demands.

\subsubsection{Fast Denoising Techniques}

\item Methods such as Non-Local Means or fast CNN-based denoising models are optimized for real-time performance.

\subsection{Energy Efficiency Considerations}
\label{subsec:energy-efficiency-considerations}


Power management techniques, especially if the Raspberry Pi will be deployed in remote or mobile environments.
Raspberry Pi’s dedicated GPU or external accelerators (e.g., Coral USB Accelerator).


\section{Proposed Solution}
\label{sec:proposed-solution}

